### 2022-01-04 intro.tex
editing
changes

The number and applications of \acp{CPS}~\cite{Rajkumar2010CPS} --- that is, systems in which a real, physical mechanism is controlled by a computer --- have exploded in later years.
This rise in popularity is in great part driven by the advent of novel wireless communication technologies as well as networking paradigms, such as cellular 5G and Edge Computing.

@@

The most straightforward approach to experimental research in \ac{NCS} use setups in which the complete system uses real hardware.
\textcite{Drew2005NCSWLAN} present \iac{NCS} model which considers both random packet delay and loss on both the sensor and actuator sides of the feedback loop; \textcite{Baumann2018LowPower}, on the other hand, develop an evaluation methodology for wireless \ac{NCS}.
Both works validate their results on physical testbeds, consisting of inverted penduli plants controlled wirelessly over IEEE 802.11 WiFi from a central computation point.
Similarly, \textcite{Li2014Wireless} implement a wireless microcontroller-based system for vibration control and validate it on a physical prototype consisting of a cantilever beam controlled over an IEEE 802.15.4 \ac{WPAN} system.
\textcite{Cuenca2019UAV} design and implement periodic event-triggered sampling and dual-rate control techniques for wireless control, validating their contributions on a four-rotor autonomous drone platform controlled over WiFi.

@@

\textcite{Zoppi2020NCSBench} made a first attempt at tackling this challenge with their \emph{NCSbench} platform.
\emph{NCSbench} is an open-source \ac{NCS} benchmarking platform designed with reproducibility in mind, built using the \citetitle{LEGOMindstormsEV3}~\cite{LEGOMindstormsEV3} platform.
It allows for easy and highly reproducible experimentation and benchmarking of \acp{NCS}, due to its low-cost, accessibility, and ease of reconfiguration.

@@

In this paper, we present thus the first fully-software-based \ac{NCS} benchmarking framework with scalability and repeatability as its main focus.
This framework is built on top of the \emph{Python 3.8}~\cite{Python3.8} language, making it highly extensible and able to harness the tremendous amount of already existing user-provided libraries and packages~\cite{pypi}.
Additionally, it is fully compatible with \emph{containerization} technologies such as \emph{Docker}~\cite{merkel2014docker}, making it suitable for automated deployment and benchmarking on industry-standard deployment using container orchestration technologies.
We name this framework \ac{CLEAVE}.

>>>>

\todo[inline, caption={}]{
    \begin{itemize}
        \item You miss a bit the balance between general introduction (really only the first paragraph), discussion of related work (almost one page) and the contribution of the paper (again one paragraph). Try to find a better balance, and the best way to do that is to shorten perhaps the discussion of related work.
        \item The aspect of edge computing is a bit missing in the intro. That is perhaps not a big problem, but you could introduce it more strongly towards the contribution part. One useful angle could be that we see more and more concepts of the ``edge'' --- near edge, far edge, telco edge etc. While edge computing is seen as important for closed loop applications in general, understanding the usefullness of such different edge concepts will become more important --- which is where Cleave can help obviously.
        \item In the intro (first paragraph) you can be a bit more specific as 5G together with edge computing is introduced to become the backbone of CPS in the future. As of today, not many CPS really run on cellular networks. That does not come out from your intro, and might require you to change the narrative of the first paragraph
    \end{itemize}
}

The number and applications of \acp{CPS}~\cite{Rajkumar2010CPS} --- that is, systems in which a real, physical mechanism is controlled by a computer --- have exploded in later years.
This rise in popularity is in great part driven by the advent of novel wireless communication technologies as well as networking paradigms, such as cellular 5G and Edge (and Fog) Computing.

@@

The most straightforward approach to experimental research in \ac{NCS} uses setups in which the complete system is built on top of real hardware.
\textcite{Drew2005NCSWLAN} present \iac{NCS} model which considers both random packet delay and loss on both the sensor and actuator sides of the feedback loop; \textcite{Baumann2018LowPower}, on the other hand, develop an evaluation methodology for wireless \ac{NCS}.
Both works validate their results on physical testbeds, consisting of inverted penduli plants controlled wirelessly over IEEE 802.11 WiFi from a central computation point.
Similarly, \textcite{Li2014Wireless} implement a wireless microcontroller-based system for vibration control and validate it on a physical prototype consisting of a cantilever beam controlled over an IEEE 802.15.4 \ac{WPAN} system.
\textcite{Cuenca2019UAV} design and implement periodic event-triggered sampling and dual-rate control techniques for wireless control, validating their contributions on a four-rotor autonomous drone platform controlled over WiFi.

@@

\textcite{Zoppi2020NCSBench} made the first (and to the best of our knowledge, the only) attempt at tackling this challenge with their \emph{NCSbench} platform.
\emph{NCSbench} is an open-source \ac{NCS} benchmarking platform designed with reproducibility in mind, built using the \citetitle{LEGOMindstormsEV3}~\cite{LEGOMindstormsEV3} platform.
It allows for easy and highly reproducible experimentation and benchmarking of \acp{NCS}, due to its low-cost, accessibility, and ease of reconfiguration.

@@

In this paper, we present thus the first fully-software-based \ac{NCS} benchmarking framework with scalability and repeatability as its main focus.
This framework is built on top of the \emph{Python 3.8}~\cite{Python3.8} language, making it highly extensible and able to harness the tremendous amount of already existing user-provided libraries and packages~\cite{pypi}.
Additionally, it is fully compatible with \emph{containerization} technologies such as \emph{Docker}~\cite{merkel2014docker}, making it suitable for automated deployment and benchmarking on industry-standard setups using container orchestration technologies.
We name this framework \ac{CLEAVE}.
